---
title: 'Project 3: Tutorial'
author: "Carl Myers"
collaborator: "Edward Sung"
output: rmarkdown::html_vignette
vienette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(PROJECT3)
```

The PROJECT3 package is a final project for STAT 302. It can be used for a variety of uses including linear modeling, k-nearest-neighbors, t-tests, and Random Forest Cross Validation. To install the package from github, run the following code.z

## Install Package from Github
```{r, eval=FALSE}
devtools::install_github("carldmyers/PROJECT3")
library(PROJECT3)
help(package = "PROJECT3", help_type = "html")
utils::browseVignettes(package = "PROJECT3")
```

# Tutorial for my_t_test()

All the tests demonstrated below use `lifeExp` data from `my_gapminder`.
# case I: alternative = "two.sided"
  \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &\neq 60.
  \end{align}
```{r}
data("my_gapminder")
my_t_test(my_gapminder$lifeExp, alternative = "two.sided", mu = 60)
```
From the test result, we notice that the p_value is greater than 0.05. Thus, it is not statistically significant have no enough evidence to reject the null hypothesis.

# case II: alternative = "less"
  \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &< 60.
  \end{align}
```{r}
my_t_test(my_gapminder$lifeExp, alternative = "less", mu = 60)
```
From the test result, we notice that the p_value is less than 0.05. Thus, it is not statistically significant have no enough evidence to reject the null hypothesis.

# case III: alternative = "greater"
  \begin{align}
  H_0: \mu &= 60,\\
  H_a: \mu &> 60.
  \end{align}
```{r}
my_t_test(my_gapminder$lifeExp, alternative = "greater", mu = 60)
```
From the test result, we notice that the p_value is greater than 0.05. Thus, it is not statistically significant have no enough evidence to reject the null hypothesis.


# Tutorial for my_lm()
```{r, eval=FALSE}
test <- my_lm(formula = lifeExp ~ gdpPercap + continent, data = my_gapminder)
my_coef <- test[, 1]
my_matrix <- model.matrix(lifeExp ~ gdpPercap + continent, data = my_gapminder)
y_hat <- my_matrix %*% as.matrix(my_coef)
my_df <- data.frame("actual" = my_gapminder$lifeExp, "fitted" = y_hat, "continent" = my_gapminder$continent)
 ggplot(my_df, aes(x = actual, y = fitted, color = continent)) +
   geom_point() +
   geom_abline(slope = 1, intercept = 0, col = "black") + 
   theme_bw(base_size = 15) +
   labs(x = "Fitted values", y = "Actual values", title = "Actual vs. Fitted") + 
   theme(plot.title = element_text(hjust = 0.5))
```
As shown, we notice that the difference of `lifeExp` between two observations is an unit in `gdpPercap`. Compared to the coeffiecients of different continents, `gdpPercap` has less influence on `lifeExp` than `continent`.

# Tutorial for my_knn_cv()
```{r}
knn_vector <- c(1 : 10)
tu_knn <- matrix(NA, nrow = 10, ncol = 3)
for (i in 1 : 10) {
  tu_knn[i, 1] <- knn_vector[i]
  # get the cv misclassification rate
  tu_knn[i, 3] <- my_knn_cv(train = my_gapminder[, 3 : 4], 
          cl = my_gapminder$continent, k_nn = knn_vector[i], k_cv = 5)$cv_err
  prediction <- my_knn_cv(train = my_gapminder[, 3 : 4], 
          cl = my_gapminder$continent, k_nn = knn_vector[i], k_cv = 5)$class
  # get tge training misclassification rate
  tu_knn[i, 2] <- sum(prediction != my_gapminder$continent) / length(my_gapminder$continent)
}
tu_knn <- data.frame("k_nn" = tu_knn[, 1], "training_misclassification_rate" = tu_knn[, 2], 
                     "CV_misclassification_rate" = tu_knn[, 3])
```


# Tutorial for my_rf_cv()
```{r}
k_vector <- c(2, 5, 10)
tu_rf <- matrix(NA, nrow = 90, ncol = 2)
for (i in 1 : length(k_vector)) {
  for (j in 1 : 30) {
    tu_rf[(i - 1) * 30 + j, 1] <- k_vector[i]
    tu_rf[(i - 1) * 30 + j, 2] <- my_rf_cv(k_vector[i])
  }
}
```


```{r}
tu <- data.frame("K_value" = tu_rf[, 1], "MSE" = tu_rf[, 2])
tu_graph <- ggplot(data = tu,
       aes(x = K_value, y = MSE, group = K_value)) +
  geom_boxplot(fill = "lightblue") +
  theme_bw(base_size = 16) +
  labs(title = "CV estimated MSE for different k-values",
       x = "k-values",
       y = "Estimated MSE") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  scale_x_continuous(breaks = c(2, 5, 10)) 
rf_vector <- c(mean(tu_rf[1 : 30, 2]), mean(tu_rf[31 : 60, 2]), mean(tu_rf[61 : 90, 2]), sd(tu_rf[1 : 30, 2]), sd(tu_rf[31 : 60, 2]), sd(tu_rf[61 : 90, 2]))
rf_matrix <- matrix(rf_vector, nrow = 3, ncol = 2)
# Use a table to display the average CV estimate and the standard deviation of the CV estimates across k
rf_table <- data.frame("k_values" = c(2, 5, 10),"mean" = rf_matrix[, 1], "sd" = rf_matrix[, 2])
```
